### 2020-11-23 article/article.tex
0.1.3, hides all GPU weird stuff from user

\section*{Paper Authors}
1. Tritt, Alexander;\\
2. Turner, Lincoln David;\\
3. Saunderson, James;\\
4. Morris, Joshua;\\
5. Hochstetter, Joel;\\

@@

\section*{Paper Author Roles and Affiliations}
1. PhD student, School of physics and astronomy, Monash University\\
2. Supervisor, School of physics and astronomy, Monash University\\
3. Supervisor, Department of electrical and computer systems engineering, Monash University\\
4. Original writer of AtomicPy for spin half systems\\
5. Original writer of the spin one extension to AtomicPy\\

>>>>

\section*{Paper Authors}
1. Tritt, Alex;\\
2. Morris, Joshua;\\
3. Hochstetter, Joel;\\
4. Anderson, R. P.;\\
5. Saunderson, James;\\
6. Turner, L. D.;\\

@@

\section*{Paper Author Roles and Affiliations}
1. School of Physics \& Astronomy, Monash University, Victoria 3800, Australia.\\
	Primary author of the released packages.\\
2. School of Physics \& Astronomy, Monash University, Victoria 3800, Australia.\\
	Present address: Faculty of Physics, University of Vienna, 1010 Vienna, Austria.\\
	Author of first version of code.\\
3. School of Physics \& Astronomy, Monash University, Victoria 3800, Australia.\\
	Present address: School of Physics, University of Sydney, NSW 2006, Australia.\\
	Optimization and extension to spin one of first version of code.\\
4. School of Molecular Sciences, La Trobe University, PO box 199, Bendigo, Victoria 3552, Australia.\\
	Original conception of first version of code.\\
5. Department of Electrical and Computer Systems Engineering, Monash University, Victoria 3800, Australia.\\
	Advice on numerical analysis.\\
6. School of Physics \& Astronomy, Monash University, Victoria 3800, Australia.\\
	Original conception of released version of algorithm.
